The Migration of the Field Code

### 2016-03-11 talks/dh-working-group/Funk-Mullen.Migration-Field-Code.working-paper.Rmd
Fix typo

By framing our historical questions around "medium data" we enjoyed a useful symbiosis of traditional and digital historical methods. Our computational methods produced useful historical knowledge because they were justified by what we knew about the data from traditional historical work. We knew that code commissioners worked with "the scissors and paste-pot,"^[*Rocky Mountain News*, January 20, 1877.] as political debates from the era frequently complained, and we knew of codes in the archives that commisions literally marked up the legislation of other states.^[The Nevada code was created by marking up a printed copy of California's code. Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.] Knowing that borrowings happened section by section justified our use of the minhash/LSH algorithm, and the nature of the borrowings justified our use of affinity propagration clustering. And knowing how codes passed from state to state made network analysis an obvious fit.^[This is an example of the "no free lunch theorem" in action. See David Robinson, "K-means clustering is not a free lunch," *Variance Explained*, January 16, 2015: <http://varianceexplained.org/r/kmeans-free-lunch/>, citing David H. Wolpert and William G. Macready, "No Free Lunch Theorems for Optimization" *IEEE Transactions on Evolutionary Computation* 1, no. 1 (April 1997): 67--82, <http://ti.arc.nasa.gov/m/profile/dhw/papers/78.pdf>.]  Our method is applicable to many historical questions and sources, especially corpora where the documents can be readily divided into sections. We may pursue it with other legal documents, such as treatises or statutes, or with sources for religious history, such as hymnbooks or tracts.

>>>>

By framing our historical questions around "medium data" we enjoyed a useful symbiosis of traditional and digital historical methods. Our computational methods produced useful historical knowledge because they were justified by what we knew about the data from traditional historical work. We knew that code commissioners worked with "the scissors and paste-pot,"^[*Rocky Mountain News*, January 20, 1877.] as political debates from the era frequently complained, and we knew of codes in the archives that commissions literally marked up the legislation of other states.^[The Nevada code was created by marking up a printed copy of California's code. Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.] Knowing that borrowings happened section by section justified our use of the minhash/LSH algorithm, and the nature of the borrowings justified our use of affinity propagation clustering. And knowing how codes passed from state to state made network analysis an obvious fit.^[This is an example of the "no free lunch theorem" in action. See David Robinson, "K-means clustering is not a free lunch," *Variance Explained*, January 16, 2015: <http://varianceexplained.org/r/kmeans-free-lunch/>, citing David H. Wolpert and William G. Macready, "No Free Lunch Theorems for Optimization" *IEEE Transactions on Evolutionary Computation* 1, no. 1 (April 1997): 67--82, <http://ti.arc.nasa.gov/m/profile/dhw/papers/78.pdf>.]  Our method is applicable to many historical questions and sources, especially corpora where the documents can be readily divided into sections. We may pursue it with other legal documents, such as treatises or statutes, or with sources for religious history, such as hymnbooks or tracts.
